### 2018-03-11 paper/2-background.tex
Minor tweaks

If the user runs \Make specifying \cmd{main.exe} as the desired output, \Make
will first build \cmd{util.o} and \cmd{main.o}, in any order since the
corresponding tasks are independent, and then build \cmd{main.exe}. If the
user modifies the sources of \cmd{util.h} and runs \Make again, it will
perform a \emph{full rebuild}, because all three tasks transitively depend on
the \cmd{util.h}, as illustrated in Fig.~\ref{fig-make}(b). On the other hand, if the
user modifies \cmd{main.c} then a \emph{partial rebuild} is sufficient:
the file \cmd{util.o} does not need to be rebuilt, since its inputs have not
changed, see Fig.~\ref{fig-make}(c). Note that if the dependency graph is
\emph{acyclic} then each task needs to be executed at most once. Cyclic task
dependencies are typically not allowed in build systems although there are rare
exceptions, see~\S\ref{sec-iterative-compute}.

@@

To achieve minimality \Make relies on two main ideas: (i) it uses \emph{file
modification time} to detect which files changed\footnote{Technically, you
can fool \Make by altering the modification time of a file without changing its
content, e.g. by using the command \cmd{touch}. \Make is therefore minimal only
under the assumption that you do not do that.}, and (ii) it constructs a
complete task dependency graph from the information contained in the makefile
and executes tasks in a \emph{topological order}. For a more concrete description
see~\S\ref{sec-implementation-make}.

>>>>

If the user runs \Make specifying \cmd{main.exe} as the desired output, \Make
will first build \cmd{util.o} and \cmd{main.o}, in any order since the
corresponding tasks are independent, and then build \cmd{main.exe}. If the
user modifies the sources of \cmd{util.h} and runs \Make again, it will
perform a \emph{full rebuild}, because all three tasks transitively depend on
\cmd{util.h}, as illustrated in Fig.~\ref{fig-make}(b). On the other hand, if
the user modifies \cmd{main.c} then a \emph{partial rebuild} is sufficient:
the file \cmd{util.o} does not need to be rebuilt, since its inputs have not
changed, see Fig.~\ref{fig-make}(c). Note that if the dependency graph is
\emph{acyclic} then each task needs to be executed at most once. Cyclic task
dependencies are typically not allowed in build systems although there are rare
exceptions, see~\S\ref{sec-iterative-compute}.

@@

To achieve minimality \Make relies on two main ideas: (i) it uses \emph{file
modification time} to detect which files changed\footnote{Technically, you
can fool \Make by altering the modification time of a file without changing its
content, e.g. by using the command \cmd{touch}. \Make is therefore minimal only
under the assumption that you do not do that.}, and (ii) it constructs a task
dependency graph from the information contained in the makefile and executes
tasks in a \emph{topological order}. For a more concrete description
see~\S\ref{sec-implementation-make}.
